Appendix S1: Supporting Tables and Figures

### 2021-09-21 ms/SI.Rmd
Fix typo that erased SI fig 11

a <- plot_genus("a", "Equisetum")
b <- plot_genus("b", "Deparia")
c <- plot_genus("c", "Cyrtomium")
d <- plot_genus("d", "Dryopteris")
e <- plot_genus("e", "Pteris")
f <- plot_genus("f", "Diplazium") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm")) +

>>>>

a <- plot_genus("a", "Equisetum")
b <- plot_genus("b", "Deparia")
c <- plot_genus("c", "Cyrtomium")
d <- plot_genus("d", "Dryopteris")
e <- plot_genus("e", "Pteris")
f <- plot_genus("f", "Diplazium") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm"))
